Coherent optical association of a single molecule

### 2020-10-30 paper.tex
Show an unaddressed comment from jon in the paper

Early experiments used weakly-bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly-bound excited state as the intermeidate state
suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
resulting in molecule loss \todo{be more clear with "molecule loss". I think you mean:
  resulting in large incoherence and loss to other molecular states.}.
This scattering is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
% With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states. Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state. The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum. (See SM)

>>>>

Early experiments used weakly-bound excited states as the intermediate state
in the Raman transition to ensure a large Raman Rabi frequency~\cite{Wynar2000,Rom2004}.
However, for a complete picture, the many excited vibrational states in a molecular potential
as well as the excited atomic continuum need to be considered.
The total scattering rate and Raman Rabi rate become a sum of the scattering rates
and Raman Rabi rates over all possible intermediate states.
With these considerations, using a weakly-bound excited state as the intermeidate state
suffers from strong scattering of the nearby excited atomic continuum rendering it incoherent,
resulting in molecule loss \text{red}{Jon: be more clear with "molecule loss". I think you mean:
  resulting in large incoherence and loss to other molecular states.}.
This scattering is proportional to $1/\delta_{thresh}^2$,
where $\delta_{thresh}$ is the detuning from the dissociation threshold,
and thus can be made smaller by using deeply bound vibrational states as the intermediate level.
% With the multiple excited vibrational states present in a molecular potential as intermediate states, the total scattering rate and Raman Rabi rate become a sum over the scattering rates and Raman Rabi rates of the individual intermediate states. Furthermore, for a more complete calculation, we also need to account for the effects of the excited atomic continuum, which is particularly important for the target molecular state. The sum of the squares of the wavefunction overlap between the target weakly-bound molecular state and all the excited molecular intermediate states considered is only about 2\%, suggesting that there is significant matrix element between the target molecular state and the excited atomic continuum. (See SM)
